Racets: Policy{-}Agnostic Programming in Racket

### 2018-07-23 paper/paper.tex
Committing some bug fixes for various macros

           e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
           e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \and
           v = \formfacet{pc}{v_1}{v_2}}

@@

@@

\[\small
\begin{array}{ccc}
  {\color{brown}
    \inferrule[\textsc{Fac-Create-Pos}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{+ \ell \in pc} \\\\
                e_2, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
  & 
  {\color{gray}
    \inferrule[\textsc{Fac-Create-Neg}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{- \ell \in pc} \\\\
                e_3, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
  &
  {\color{purple}
    \inferrule[\textsc{Fac-Create-Split}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{\{+\ell, -\ell\} \cap pc = \varnothing} \\\\
                e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
                e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \and
                v = \formfacet{pc}{v_1}{v_2}}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}

@@

\begin{figure}
{\small
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets]
(define-syntax-rule (fac l e1 e2)
  (cond
\end{lstlisting}
\vspace{-.7\baselineskip}
{\color{brown}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{brown}]
    [(set-member? (current-pc) (pos (facet-labelname l))) e1]
\end{lstlisting}
}
\vspace{-.7\baselineskip}
{\color{gray}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{gray}]
    [(set-member? (current-pc) (neg (facet-labelname l))) e2]
\end{lstlisting}
}
\vspace{-.7\baselineskip}
{\small\color{purple}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{purple},keywordstyle=\color{purple}]
    [else
     (let ([left (parameterize
                     ([current-pc (set-add (current-pc)
                                           (pos (facet-labelname l)))]))]
           [right (parameterize
                      ([current-pc (set-add (current-pc)
                                            (neg (facet-labelname l)))]))]
           (mkfacet (labelpair-name l) v1 v2)))]))
\end{lstlisting}}
}
\caption{Facet creation as a macro}
\label{fig:fac-create}
\end{figure}

>>>>

           e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \and
           e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \\\\
           v = \formfacet{pc \cup \{+\ell\}}{v_1}{v_2}}

@@

          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \\\\

@@

\kris{TODO: FIX THIS (make consistent w semantics)}
\[\small
\begin{array}{ccc}
  {\color{brown}
    \inferrule[\textsc{Fac-Create-Pos}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{+ \ell \in pc} \\\\
                e_2, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
  & 
  {\color{gray}
    \inferrule[\textsc{Fac-Create-Neg}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{- \ell \in pc} \\\\
                e_3, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
  &
  {\color{purple}
    \inferrule[\textsc{Fac-Create-Split}]
              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
                \boxed{\{+\ell, -\ell\} \cap pc = \varnothing} \\\\
                e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
                e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \and
                v = \formfacet{pc}{v_1}{v_2}}
              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}

@@

\begin{figure}
{\small
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets]
(define-syntax-rule (fac l e1 e2)
  (cond
\end{lstlisting}
\vspace{-.7\baselineskip}
{\color{brown}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{brown}]
    [(set-member? (current-pc) (pos (facet-labelname l))) e1]
\end{lstlisting}
}
\vspace{-.7\baselineskip}
{\color{gray}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{gray}]
    [(set-member? (current-pc) (neg (facet-labelname l))) e2]
\end{lstlisting}
}
\vspace{-.7\baselineskip}
{\small\color{purple}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{purple},keywordstyle=\color{purple}]
    [else
     (let ([left (parameterize
                     ([current-pc (set-add (current-pc)
                                           (pos (facet-labelname l)))]))]
           [right (parameterize
                      ([current-pc (set-add (current-pc)
                                            (neg (facet-labelname l)))]))])
           (mkfacet (set-union (set (pos (labelpair-name l)))
                                    (current-pc))
                    v1 v2))]))
\end{lstlisting}}
}
\caption{Facet creation as a macro}
\label{fig:fac-create}
\end{figure}
